The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2023-05-15 MS_ToSubmit/MS_Burdwood_foodweb.tex
References tidying

The evidence of benefits provided by Marine Protected Areas (MPAs) as
well as the urgent need for ocean protection have driven an
unprecedented increase in the number of MPAs worldwide in recent years
(Roberts et al., 2017; Sala et al., 2018). Globally, the total area of
the world ocean designated under marine protection adds up to
approximately 29,600,000 km\textsuperscript{2}, distributed across
nearly 18,444 MPAs and covering 8.16\% of the ocean's surface (IUCN \&
UNEP-WCMC, 2023), and therefore approaching the 10\% goal of the
Convention of Biological Diversity (CBD, 2004). Despite this progress,
recent reports have shown that actual protection has been overestimated
because it includes areas that are not yet effectively protected (only
declared) as well as areas that allow significant extractive activities
(Sala et al., 2018).

@@

Many of these MPAs focus on the presence of particularly vulnerable,
keystone, or charismatic species, large numbers (or proportions) of
endemic species, and/or high biodiversity across taxonomic levels (Hogg
et al., 2016). Indeed, the MPA N-BB was created to protect a sensitive
and biodiverse benthic habitat that was barely known (Falabella, 2017;
Schejter et al., 2016). The benthic community is featured by high
biomass of vulnerable and fragile species (mainly Porifera and Cnidaria)
that meet the characteristics of vulnerable marine ecosystems (Schejter
\& Albano, 2021), here defined as sites that present taxa with a minimum
biomass of 10 kg per 1200 m\textsuperscript{2} (Commission for the
Conservation of Antarctic Marine Living Resources, 2009). Also, it
provides habitat to several small-sized species (López-Gappa et al.,
2018; Schejter \& Bremec, 2019; Sirito, 2019), and has an important role
in the life history of fishes as a food source, refuge and nursery area
(Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al., 2022;
Florencia et al., 2023; García Alonso et al., 2018; Troccoli et al.,
2020; Vazquez et al., 2018). The maintenance of this singular community
is related to local and regional oceanographic processes, including the
circulation of the rich Malvinas (Falkland) current in the area
(Guerrero et al., 1999; Piola \& Gordon, 1989) and the upwelling and
mixing phenomena (Matano et al., 2019). The input of nutrients from the
Malvinas (Falkland) current also supports a diverse plankton community
(Guinder et al., 2020). Overall, 811 benthic and plankton species have
been identified for the MPA N-BB ecosystem, where 349 were reported for
the first time in the area in recent years (Administracion de Parques
Nacionales, 2022). However, identifying the main species involved in the
maintenance of ecosystem services and health as well as for management
and conservation is essential.

@@

High-latitude marine ecosystems, such as the MPA N-BB, are considered
complex systems in terms of biodiversity and ecological interactions
(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
et al., 2021). Although there is a robust knowledge about the complexity
considering the richness of the benthic and plankton communities in the
MPA N-BB ecosystem (Administracion de Parques Nacionales, 2022; Guinder
et al., 2020; Schejter et al., 2016, 2020), a better understanding of
species interactions' complexity and structure is needed. This aspect
can be tackled by analysing one of the most frequent relationships
between species: the predator-prey interaction (Bascompte, 2009). The
sum of predator-prey or trophic interactions of a particular region is
referred to as a food web, representing the roadmap for matter and
energy flow in an ecosystem. In recent years, network approaches have
been successfully applied to study complex high-latitude marine
ecosystems, improving our knowledge on structure, functioning, and
response to environmental/anthropogenic changes (Cordone et al., 2018;
Funes et al., 2022; Kortsch et al., 2015; Marina et al., 2023). Among
anthropogenic threats, it is worth mentioning that contaminants like
mercury and microplastics have been recently reported as important
threats to the MPA N-BB region (Cossi et al., 2021; Di Mauro et al.,
2022; Fioramonti et al., 2022); also fishing vessels are allowed to
operate in the western section of the MPA N-BB (i.e.~Marine National
Reserve category), altering the stocks of commercially important fish
species (Administracion de Parques Nacionales, 2022; Martínez et al.,
2021). Moreover, there is a potential hazard related to the effects of
offshore activities (exploration and explotation) to the west of the MPA
N-BB (Administracion de Parques Nacionales, 2022).

@@

The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws
26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau
called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth,
N-BB I and N-BB II, respectively (Administracion de Parques Nacionales,
2023; Tombesi et al., 2020) (Figure 1). They are located 150 km east of
Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
MPA N-BB I comprises nearly 34,000 km\textsuperscript{2} circumscribed
by the 200 m isobath, between 54º--55ºS and 56º--62ºW, with a slight
slope extended nearly 370 km east--west. Physical features in the BB are
fairly stable, with salinity averaging 34 all year round and temperature
ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999;
Piola \& Falabella, 2009). The BB is surrounded by steep flanks of up to
4000 m depth through which strong currents circulate (Matano et al.,
2019; Piola \& Gordon, 1989; Reta, 2014). The N-BB II includes such a
deep slope, protecting about 32,000 km\textsuperscript{2}. Intense
upwelling and mixing occur over it, entraining deep nutrient-rich waters
into the photic layer (Matano et al., 2019; Piola \& Falabella, 2009)
and resulting in a fairly homogeneous water column both spatially and
temporally (Glorioso \& Flather, 1995; Guerrero et al., 1999; Matano et
al., 2019).

Given the evidence collected during several research cruises about the
oceanographic and ecological processes connecting MPAs N-BB I and II
(references in Administracion de Parques Nacionales, 2022), a joint
management plan was recently proposed (Administracion de Parques
Nacionales, 2022). This is why, the study area of the present work
includes both MPAs.

@@

The food web studied in the present work might be more representative of
the shallow ecosystem of the submarine plateau called Burdwood Bank, on
which most of the research was focused as the MPA N-BB I was first
created. This is related to the sampling effort that was conducted
during the research cruises in the former MPA compared to the MPA N-BB
II (i.e.~deep flanks to the south). As a consequence, most of the data
we used to build the network come from studies performed in the MPA N-BB
I. Despite this fact, we decided to build the food web considering both
MPAs due to the tight oceanographic and ecological connection that
exists among them (Administracion de Parques Nacionales, 2022 and
references therein).

@@

\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2022}{}}%
Administracion de Parques Nacionales. (2022). \emph{Plan de gestión {AMP
Namuncurá Banco Burdwood}}.

\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2023}{}}%
Administracion de Parques Nacionales. (2023). \emph{Área {Marina
Protegida Namuncurá Banco Burdwood}}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2019}{}}%
Belleggia, M., Battagliotti, C., Cortés, F., \& Colonello, J. H. (2019).
Feeding together: A global diet analysis of twenty-three species of
chondrichthyes on a feeding ground area. \emph{Hydrobiologia},
\emph{842}(1), 77--99. \url{https://doi.org/10.1007/s10750-019-04027-w}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2019}{}}%
Bergagna, L. (2019). \emph{{Descripción de los ensambles bentónicos del
AMP Namuncurá-Banco Burdwood y estimación del contenido de carbono
-orgánico e inorgánico- allí presente.}} {[}\{Bachelor Thesis\}{]}.
Universidad Nacional de Córdoba.

\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2020}{}}%
Bergagna, L., Chiesa, I., Álvarez, Y. P., Ceballos, S. G., Boy, C. C.,
Riccialdelli, L., \& Lovrich, G. A. (2020). {En el fondo el Banco es
bueno}. \emph{La Lupa. Colección Fueguina de Divulgación Científica},
\emph{16}, 20--24.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Borrelli2014}{}}%
Borrelli, J. J., \& Ginzburg, L. R. (2014). Why there are so few trophic
levels: {Selection} against instability explains the pattern. \emph{Food
Webs}, \emph{1}(1), 10--17.
\url{https://doi.org/10.1016/j.fooweb.2014.11.002}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Brickle2009}{}}%
Brickle, P., Arkhipkin, A. I., Laptikhovsky, V., Stocks, A., \& Taylor,
A. (2009). Resource partitioning by two large planktivorous fishes
{Micromesistius} australis and {Macruronus} magellanicus in the
{Southwest Atlantic}. \emph{Estuarine, Coastal and Shelf Science},
\emph{84}(1), 91--98. \url{https://doi.org/10.1016/j.ecss.2009.06.007}

@@

\leavevmode\vadjust pre{\hypertarget{ref-CBD2004}{}}%
CBD. (2004). \emph{Secretariat of the convention on biological
diversity: {Technical} advice on the establishment and management of a
national system of marine and coastal protected areas, {Technical
Series} number 13.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-AlvarezColombo2018}{}}%
Colombo, G. Álvarez. (2018). \emph{{Informe de Campaña Namuncurá-Banco
Burdwood: \textquestiondown Area de cría de peces australes?}} (p. 83)
{[}\{Field campaign Report\}{]}.

\leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResources2009}{}}%
Commission for the Conservation of Antarctic Marine Living Resources.
(2009). \emph{Vulnerable {Marine Ecosystem} taxa identification guide}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2015}{}}%
Dellabianca, N. A. (2015). \emph{{Informe de Campaña {``Namuncurá-Banco
Burdwood''}}} (p. 48) {[}\{Field campaign Report\}{]}.

\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2018}{}}%
Dellabianca, N. A. (2018). \emph{{Informe de Campaña AMP Namuncurá
\textendash{} Banco Burdwood: Comprendiendo la bomba biológica de
carbono}} (p. 101) {[}\{Field campaign Report\}{]}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Estrada2007}{}}%
Estrada, E. (2007). Food webs robustness to biodiversity loss: {The}
roles of connectance, expansibility and degree distribution.
\emph{Journal of Theoretical Biology}, \emph{244}(2), 296--307.
\url{https://doi.org/10.1016/j.jtbi.2006.08.002}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2021}{}}%
Fernández, M., Rodríguez-Ruiz, M., Gelcich, S., Hiriart-Bertrand, L., \&
Castilla, J. C. (2021). Advances and challenges in marine conservation
in {Chile}: {A} regional and global comparison. \emph{Aquatic
Conservation: Marine and Freshwater Ecosystems}, \emph{31}(7),
1760--1771. \url{https://doi.org/10.1002/aqc.3570}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
Franco, B. C., Defeo, O., Piola, A. R., Barreiro, M., Yang, H., Ortega,
L., Gianelli, I., Castello, J. P., Vera, C., Buratti, C., Pájaro, M.,
Pezzi, L. P., \& Möller, O. O. (2020). Climate change impacts on the
atmospheric circulation, ocean, and fisheries in the southwest {South
Atlantic Ocean}: A review. \emph{Climatic Change}, \emph{162}(4),
2359--2377. \url{https://doi.org/10.1007/s10584-020-02783-6}

\leavevmode\vadjust pre{\hypertarget{ref-Freeman1978}{}}%
Freeman, L. C. (1978). Centrality in social networks conceptual
clarification. \emph{Social Networks}, \emph{1}(3), 215--239.
\url{https://doi.org/10.1016/0378-8733(78)90021-7}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Giberto2017}{}}%
Giberto, D. A., Belleggia, M., \& Bremec, C. S. (2017). \emph{El bentos
como alimento de peces comerciales.} {Instituto Nacional de
Investigación y Desarrollo Pesquero (INIDEP)}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Grilli2016}{}}%
Grilli, J., Rogers, T., \& Allesina, S. (2016). Modularity and stability
in ecological communities. \emph{Nature Communications}, \emph{7}(1),
12031. \url{https://doi.org/10.1038/ncomms12031}

@@

\leavevmode\vadjust pre{\hypertarget{ref-IUCN2023}{}}%
IUCN, \& UNEP-WCMC. (2023). \emph{The world database on protected areas
({WDPA})}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2021}{}}%
Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
Bonsdorff, E., Ojaveer, H., Jurgensone, I., Strāķe, S., Rubene, G.,
Krūze, Ē., \& Nordström, M. C. (2021). Disentangling temporal food web
dynamics facilitates understanding of ecosystem functioning.
\emph{Journal of Animal Ecology}, \emph{90}(5), 1205--1216.
\url{https://doi.org/10.1111/1365-2656.13447}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Kreps2016}{}}%
Kreps, G. (2016). \emph{{Informe de Campaña AMP Namuncurá - Banco
Burdwood: Primavera 2016}} (p. 103) {[}\{Field campaign Report\}{]}.

\leavevmode\vadjust pre{\hypertarget{ref-LaMesa2016}{}}%
La Mesa, M., Riginella, E., Melli, V., Bartolini, F., \& Mazzoldi, C.
(2016). Biological traits of a sub-{Antarctic} nototheniid,
{Patagonotothen} ramsayi, from the {Burdwood Bank}. \emph{Polar
Biology}, \emph{39}(1), 103--111.
\url{https://doi.org/10.1007/s00300-015-1663-6}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martin2015}{}}%
Martin, J. (2015). \emph{{Informe de Campaña Banco Burdwood/Namuncurá
\textendash{} Tierra del Fuego}} (p. 78) {[}\{Field campaign
Report\}{]}.

\leavevmode\vadjust pre{\hypertarget{ref-Martin2021}{}}%
Martin, J., \& Flores Melo, X. (2021). \emph{{Área Marina Protegida
Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}.
{Administración de Parques Nacionales}.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez1992}{}}%
Martinez, N. D. (1992). Constant {Connectance} in {Community Food Webs}.
\emph{The American Naturalist}, \emph{139}(6), 1208--1218.
\url{https://doi.org/10.1086/285382}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2021}{}}%
Martínez, P. A., Wöhler, O. C., Troccoli, G. H., \& Di Marco, E. J.
(2021). \emph{{Análisis del impacto potencial provocado por el
establecimiento de las áreas marinas protegidas Namuncurá-Banco Burdwood
I, II y Yaganes en la pesquería argentina de merluza negra (Dissostichus
eleginoides)}} (\{Technical report\} No. 23/2021; p. 17). {Instituto
Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
report\} No. 11/15; p. 12). {Instituto Nacional de Investigación y
Desarrollo Pesquero (INIDEP)}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Matusevich2022}{}}%
Matusevich. (2022). \emph{Chondrichthyan fauna from the {Marine
Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
grounds}. https://www.researchsquare.com.
\url{https://doi.org/10.21203/rs.3.rs-2247873/v1}

\leavevmode\vadjust pre{\hypertarget{ref-May1973}{}}%
May, R. (1973). \emph{Stability and complexity in model ecosystems}.
{Princeton University Press}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Ospina-Alvarez2020}{}}%
Ospina-Alvarez, A., de Juan, S., Alós, J., Basterretxea, G.,
Alonso-Fernández, A., Follana-Berná, G., Palmer, M., \& Catalán, I.
(2020). {MPA} network design based on graph theory and emergent
properties of larval dispersal. \emph{Marine Ecology Progress Series},
\emph{650}, 309--326. \url{https://doi.org/10.3354/meps13399}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Pastorino2019}{}}%
Pastorino, G. (2019). A new deep water gastropod of the genus
{Parabuccinum} ({Neogastropoda}: {Buccinulidae}) from southwestern
{Atlantic} waters with new data on the distribution of all species.
\emph{Marine Biodiversity}, \emph{49}(2), 913--922.
\url{https://doi.org/10.1007/s12526-018-0876-7}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
Reta, R. (2014). \emph{Oceanografía del {Banco Burdwood}: {Estado
Actual} del {Conocimiento} y {Perspectivas}}. {INIDEP}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Schejter2017}{}}%
Schejter, L. (2017). \emph{{Informe de Campaña Banco Burdwood}} (p. 296)
{[}\{Field campaign Report\}{]}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
Sirito, M. (2019). \emph{Fauna asociada a corales ({Octocorallia}) e
hidroides ({Hydrozoa}) del {Área Marina Protegida} {``{Namuncurá}''}
({Banco Burdwood}) y zonas profundas adyacentes} {[}PhD thesis{]}.
Universidad Nacional de Mar del Plata.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Strogatz2001}{}}%
Strogatz, S. H. (2001). Exploring complex networks. \emph{Nature},
\emph{410}(6825), 268--276. \url{https://doi.org/10.1038/35065725}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Tilman1996}{}}%
Tilman, D. (1996). Biodiversity: {Population Versus Ecosystem
Stability}. \emph{Ecology}, \emph{77}(2), 350--363.
\url{https://doi.org/10.2307/2265614}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Woodward2005}{}}%
Woodward, G., Ebenman, B., Emmerson, M., Montoya, J. M., Olesen, J. M.,
Valido, A., \& Warren, P. H. (2005). Body size in ecological networks.
\emph{Trends in Ecology \& Evolution}, \emph{20}(7), 402--409.
\url{https://doi.org/10.1016/j.tree.2005.04.005}

>>>>

The evidence of benefits provided by Marine Protected Areas (MPAs) as
well as the urgent need for ocean protection have driven an
unprecedented increase in the number of MPAs worldwide in recent years
(Roberts et al., 2017; Sala et al., 2018). Globally, the total area of
the world ocean designated under marine protection adds up to
approximately 29,600,000 km\textsuperscript{2}, distributed across
nearly 18,444 MPAs and covering 8.16\% of the ocean's surface (IUCN \&
UNEP-WCMC, 2023), and therefore approaching the 10\% goal of the
Convention of Biological Diversity (Secretariat of the convention on
biological diversity, 2004). Despite this progress, recent reports have
shown that actual protection has been overestimated because it includes
areas that are not yet effectively protected (only declared) as well as
areas that allow significant extractive activities (Sala et al., 2018).

@@

Many of these MPAs focus on the presence of particularly vulnerable,
keystone, or charismatic species, large numbers (or proportions) of
endemic species, and/or high biodiversity across taxonomic levels (Hogg
et al., 2016). Indeed, the MPA N-BB was created to protect a sensitive
and biodiverse benthic habitat that was barely known (Falabella, 2017;
Schejter et al., 2016). The benthic community is featured by high
biomass of vulnerable and fragile species (mainly Porifera and Cnidaria)
that meet the characteristics of vulnerable marine ecosystems (Schejter
\& Albano, 2021), here defined as sites that present taxa with a minimum
biomass of 10 kg per 1200 m\textsuperscript{2} (Commission for the
Conservation of Antarctic Marine Living Resources (CCAMLR), 2009). Also,
it provides habitat to several small-sized species (López-Gappa et al.,
2018; Martin Sirito, 2019; Schejter \& Bremec, 2019), and has an
important role in the life history of fishes as a food source, refuge
and nursery area (Covatti Ale et al., 2022; Delpiani et al., 2020;
Fischer et al., 2022; Florencia et al., 2023; García Alonso et al.,
2018; Troccoli et al., 2020; Vazquez et al., 2018). The maintenance of
this singular community is related to local and regional oceanographic
processes, including the circulation of the rich Malvinas (Falkland)
current in the area (Guerrero et al., 1999; Piola \& Gordon, 1989) and
the upwelling and mixing phenomena (Matano et al., 2019). The input of
nutrients from the Malvinas (Falkland) current also supports a diverse
plankton community (Guinder et al., 2020). Overall, 811 benthic and
plankton species have been identified for the MPA N-BB ecosystem, where
349 were reported for the first time in the area in recent years
(Administración de Parques Nacionales, 2022). However, identifying the
main species involved in the maintenance of ecosystem services and
health as well as for management and conservation is essential.

@@

High-latitude marine ecosystems, such as the MPA N-BB, are considered
complex systems in terms of biodiversity and ecological interactions
(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
et al., 2021). Although there is a robust knowledge about the complexity
considering the richness of the benthic and plankton communities in the
MPA N-BB ecosystem (Administración de Parques Nacionales, 2022; Guinder
et al., 2020; Schejter et al., 2016, 2020), a better understanding of
species interactions' complexity and structure is needed. This aspect
can be tackled by analysing one of the most frequent relationships
between species: the predator-prey interaction (Bascompte, 2009). The
sum of predator-prey or trophic interactions of a particular region is
referred to as a food web, representing the roadmap for matter and
energy flow in an ecosystem. In recent years, network approaches have
been successfully applied to study complex high-latitude marine
ecosystems, improving our knowledge on structure, functioning, and
response to environmental/anthropogenic changes (Cordone et al., 2018;
Funes et al., 2022; Kortsch et al., 2015; Marina et al., 2023). Among
anthropogenic threats, it is worth mentioning that contaminants like
mercury and microplastics have been recently reported as important
threats to the MPA N-BB region (Cossi et al., 2021; Di Mauro et al.,
2022; Fioramonti et al., 2022); also fishing vessels are allowed to
operate in the western section of the MPA N-BB (i.e.~Marine National
Reserve category), altering the stocks of commercially important fish
species (Administración de Parques Nacionales, 2022; Martínez et al.,
2021). Moreover, there is a potential hazard related to the effects of
offshore activities (exploration and explotation) to the west of the MPA
N-BB (Administración de Parques Nacionales, 2022).

@@

The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws
26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau
called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth,
N-BB I and N-BB II, respectively (Administración de Parques Nacionales,
2022; Tombesi et al., 2020) (Figure 1). They are located 150 km east of
Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
MPA N-BB I comprises nearly 34,000 km\textsuperscript{2} circumscribed
by the 200 m isobath, between 54º--55ºS and 56º--62ºW, with a slight
slope extended nearly 370 km east--west. Physical features in the BB are
fairly stable, with salinity averaging 34 all year round and temperature
ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999;
Piola \& Falabella, 2009). The BB is surrounded by steep flanks of up to
4000 m depth through which strong currents circulate (Matano et al.,
2019; Piola \& Gordon, 1989; Reta, 2014). The N-BB II includes such a
deep slope, protecting about 32,000 km\textsuperscript{2}. Intense
upwelling and mixing occur over it, entraining deep nutrient-rich waters
into the photic layer (Matano et al., 2019; Piola \& Falabella, 2009)
and resulting in a fairly homogeneous water column both spatially and
temporally (Glorioso \& Flather, 1995; Guerrero et al., 1999; Matano et
al., 2019).

Given the evidence collected during several research cruises about the
oceanographic and ecological processes connecting MPAs N-BB I and II
(references in Administración de Parques Nacionales, 2022), a joint
management plan was recently proposed (Administración de Parques
Nacionales, 2022). This is why, the study area of the present work
includes both MPAs.

@@

The food web studied in the present work might be more representative of
the shallow ecosystem of the submarine plateau called Burdwood Bank, on
which most of the research was focused as the MPA N-BB I was first
created. This is related to the sampling effort that was conducted
during the research cruises in the former MPA compared to the MPA N-BB
II (i.e.~deep flanks to the south). As a consequence, most of the data
we used to build the network come from studies performed in the MPA N-BB
I. Despite this fact, we decided to build the food web considering both
MPAs due to the tight oceanographic and ecological connection that
exists among them (Administración de Parques Nacionales, 2022 and
references therein).

@@

\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2022}{}}%
Administración de Parques Nacionales. (2022). \emph{{Plan de gestión AMP
Namuncurá Banco Burdwood}}. {Dirección Nacional de Áreas Marinas
Protegidas (DNAMP), Argentina}.

@@

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009}{}}%
Commission for the Conservation of Antarctic Marine Living Resources
(CCAMLR). (2009). \emph{Vulnerable {Marine Ecosystem} taxa
identification guide}. {Commission for the Conservation of Antarctic
Marine Living Resources}.

@@

@@

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-IUCN2023}{}}%
IUCN, \& UNEP-WCMC. (2023). \emph{The world database on protected areas
({WDPA})}. {Protected Planet}.

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martin2021}{}}%
Martin, J., \& Flores Melo, X. (2021). \emph{{Área Marina Protegida
Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}. {Tercer
taller científico sobre el Área Marina Protegida Namuncurá Banco
Burdwood. Administración de Parques Nacionales (APN), Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
Martin Sirito, S. (2019). \emph{{Fauna asociada a corales (Octocorallia)
e hidroides (Hydrozoa) del Área Marina Protegida {``Namuncurá''} (Banco
Burdwood) y zonas profundas adyacentes}} {[}PhD thesis{]}. Universidad
Nacional de Mar del Plata (UNMdP), Argentina.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2021}{}}%
Martínez, P. A., Wöhler, O. C., Troccoli, G. H., \& Di Marco, E. J.
(2021). \emph{{Análisis del impacto potencial provocado por el
establecimiento de las áreas marinas protegidas Namuncurá-Banco Burdwood
I, II y Yaganes en la pesquería argentina de merluza negra (Dissostichus
eleginoides)}} (\{Technical report\} No. 23/2021; p. 17). {Instituto
Nacional de Investigación y Desarrollo Pesquero (INIDEP), Argentina}.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
report\} No. 11/15; p. 12). {Instituto Nacional de Investigación y
Desarrollo Pesquero (INIDEP), Argentina}.

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
Reta, R. (2014). \emph{Oceanografía del {Banco Burdwood}: {Estado
Actual} del {Conocimiento} y {Perspectivas}}. {Instituto Nacional de
Investigación y Desarrollo Pesquero (INIDEP), Argentina}.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Secretariatoftheconventiononbiologicaldiversity2004}{}}%
Secretariat of the convention on biological diversity. (2004).
\emph{Technical advice on the establishment and management of a national
system of marine and coastal protected areas} (Technical Report No. 13).

@@

@@

@@
